---
title: "Example of common use of the gethr package"
author: "Vicente García Díaz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example of common use of the gethr package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# hola

```{r}
library(jsonlite)
library(httr)
library(gethr)
```

```{r echo = FALSE, results = "hide"}
personal_lockAccount("0x6b637c3aadb5244ef5a2274d42e8dc34d1f9e7f3")
miner_stop()
```

```{r}
admin_datadir()
```

```{r}
web3_clientVersion()
```

Para ver las cuentas que se encuentran disponisbles en el sistema ejecutaremos la siguiente instrucción:

```{r}
eth_accounts()
```

A continuación se creará una nueva cuenta en el sistema con la API _personal_

```{r}
#personal_newAccount("my_password")
```

ffrfrf

```{r}
eth_getBalance("0xb117a8bc3ecf2c3f006b89da6826e49b4193977a")
eth_getBalance("0x10b8ed7a9603d226bfcebbffb90257e1dcc58505")
```

TODO

```{r}
eth_sendTransaction(from = "0x6b637c3aadb5244ef5a2274d42e8dc34d1f9e7f3", to = "0x10b8ed7a9603d226bfcebbffb90257e1dcc58505", value = 5)
```

TODO

```{r}
personal_unlockAccount("0x6b637c3aadb5244ef5a2274d42e8dc34d1f9e7f3", "ps")
```

TODO

```{r}
eth_sendTransaction(from = "0x6b637c3aadb5244ef5a2274d42e8dc34d1f9e7f3", to = "0x10b8ed7a9603d226bfcebbffb90257e1dcc58505", value = 5)
```

TODO

```{r}
eth_getBalance("0xb117a8bc3ecf2c3f006b89da6826e49b4193977a")
eth_getBalance("0x10b8ed7a9603d226bfcebbffb90257e1dcc58505")
```

TODO

```{r}
miner_start()
```

Vignettess are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
